\Title

### 2021-01-27 manuscript/manuscript.tex
Tweaks to discussion of the location of sources

Our gradient boosting algorithm for overlapping windows is similar to the
``bootstrap inversion'' used in \citet{vonfrese1988}, which also iteratively
fits portions of an equivalent source model to the data residuals.
The key differences are:
(1) the sources in the overlapping portions of the windows are fit more than
once, allowing the algorithm to self-correct for poor solutions to any given
window;
(2) using only data points within the window when fitting the data enables the
use of larger datasets;
(3) experience shows that the step size parameter improves the convergence of
the solution, particularly when using only the data inside the windows for
fitting.

@@

A large number of evenly distributed sources along the survey region are
capable of reproducing the observed data.
Nevertheless, the computational load can be prohibitive and such
underdetermined problems are prone to overfiting the data, leading to poor
predictive power when interpolating and extrapolating.
On the other hand, using few sources will reduce the computational requirements
but the model may be incapable of reproducing the full spectral content of the
measured data.

@@

\begin{equation}
  z = z_{obs} + \Delta z + \alpha h,
\end{equation}

@@

Figures~\ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences} show that all source distributions
produce accurate predictions, both for the ground and airborne survey.
The RMS scores don't show significant difference, so we can only conclude
that all the source distributions are able to produce comparable predictions.
Nevertheless, the \emph{block averaged sources} make use of less sources to
produce this predictions, what would reduce the computational load needed to
fit the sources coefficients and finally compute the actual prediction.

The RMS doesn't seem to depend on the choice of the depth strategy used to
locate the equivalent sources.
At first glance, the choice of a depth strategy doesn't seem to impact the
computational needs.
Nevertheless, when trying to find the set of parameters that produce the most
accurate predictions through a method like cross-validation, we need to fit the
source coefficients one time per every possible combination of parameters.
A depth strategy like the \emph{variable depth} needs a higher number of
parameters (depth, depth factor, K nearest) than \emph{constant depth} or
\emph{relative depth} (which takes only a depth parameter).
The addition of these new parameters makes the search of the best set more
computationally expensive: more parameters means increasing the dimensions of
the parameters space and thus increasing the number of possible combinations.
Therefore we would be more prone to choose a \emph{constant depth} or
a \emph{relative depth} when dealing with very large datasets in order to save
some computation time.

>>>>

Our gradient boosting algorithm for overlapping windows is similar to the
``bootstrap inversion'' used in \citet{vonfrese1988}, which also iteratively
fits portions of an equivalent source model to the data residuals.
The key differences are that in our method:
(1) the sources in the overlapping portions of the windows are
fit more than once, allowing the algorithm to self-correct for poor solutions
to any given window;
(2) we use only data points within the window when fitting the data enables the
use of larger datasets;
(3) experience shows that the step size parameter improves the convergence of
the solution, particularly when using only the data inside the windows for
fitting.

@@

A large number of evenly distributed sources along the survey region are
capable of reproducing the observed data.
Nevertheless, the computational load can be prohibitive and such
underdetermined problems are prone to overfitting the data, leading to poor
predictive power when interpolating and extrapolating.
On the other hand, using few sources will reduce the computational requirements
but the model may be incapable of reproducing the full spectral content of the
measured data.

@@

\begin{equation}
  z = z_{obs} + \Delta z + \alpha h,
  \label{eq:variable_depth}
\end{equation}

@@

Figures~\ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences} show that there are no significant
differences between source distribution strategies, both in terms of the
interpolation RMS errors and from visual inspection of the difference maps.
Therefore, we argue that all source distribution strategies are able to produce
comparably accurate interpolations.
Nevertheless, the \emph{block-averaged-sources} strategy make use of fewer
sources to when compared with other strategies, which reduces the computational
load of estimating the sources coefficients and forward modelling.

The choice of source depth strategy does not appear to impact the interpolation
RMS error.
At a first glance, the choice of a depth strategy also would not seem to impact
the computation time.
However, when searching for the set of hyper-parameters that produce the most
accurate interpolation (e.g., through cross-validation), one must solve the
inverse problem once for every possible combination of parameters.
A depth strategy like the \emph{variable depth} requires a higher number of
hyper-parameters (depth shift $\Delta z$, depth factor $\alpha$, and the number
of nearest neighbours $k$ from Eq.~\ref{eq:variable_depth}) than other
strategies which only require a single parameter.
Having more parameters means increasing the dimensions of the parameter space
and thus increasing the number of possible combinations.
Thus, we recommend using a \emph{constant depth} or a \emph{relative depth}
when processing large datasets in order to minimize computation time.
